On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-05-22 Manuscript/manuscript.tex
Updated BCA Procedure

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
\eds{a different abbrevation/notation was used for this in the introduction}
\mc{used $BC_a$}
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, and let
$\hat{\theta}_{n, -i}$ be the jackknife values of $Z_{(i)}$
for $i \in \{1, \ldots, n\}$, 
and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
$\hat\theta_{BC_a}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} +
  z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$
\eds{notation will need to be cleaned and clarified}
A $(1 - \alpha)$ centered $BC_a$ CI is
\[
(\hat\theta_{BC_a}[\alpha/2], \quad
\hat\theta_{BC_a}[1 - \alpha/2]).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the 
rate of change of of the standard error of $\hat\theta_n$ with respect to
$\theta$.

>>>>

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
\eds{a different abbrevation/notation was used for this in the introduction}
\mc{used $BC_a$}
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, let
$\hat{\theta}_{(i)}$ be the jackknife values of $Z_{(i)}$
for $i \in \{1, \ldots, n\}$, 
and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} - \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} - \hat{\theta}_{(i)})^2\}^{3/2}}
.\] For a $1 - \alpha$ CI, let
\[
\alpha_1 = \Phi(z_0 + \frac{z_{0} +
  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}).
\]
\[
\alpha_2 = \Phi(z_0 + \frac{z_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}).
\]
\eds{notation will need to be cleaned and clarified}
A $(1 - \alpha) BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the 
rate of change of of the standard error of $\hat\theta_n$ with respect to
$\theta$.
